---
title: "GenBank BLAST Analysis Report"
author: "Matteo"
date: "2025-02-25"
output: html_document
---

This report analyzes a given DNA sequence using BLAST to identify the closest matching organism in GenBank.

```{r}
library(rentrez)
library(BiocManager)
BiocManager::install(c("annotate", "Biostrings", "sangerseqR"), ask = FALSE)
library(annotate)
library(Biostrings)
library(sangerseqR)
```

```{r}
sequence <- "GCCTGATGGAGGGGGATAACTACTGGAAACGGTAGCTAATACCGCATGACTCTGCAAGAGCAAAGTGGGGGACCTTAGGGCCTCACGCCATCGGATGAACCCAGATGGGATTAGCTAGTAGGTGGGGTAATGGCTCACCTAGGCGACGATCCCTAGCTGGTCTGAGAGGATGACCAGCCACACTGGAACTGAGACACGGTCCAGACTCCTACGGGAGGCAGCAGTGGGGAATATTGCACAATGGGCGCAA"

sequence <- gsub("\\n", "", sequence)
dna_seq <- DNAString(sequence)
```

```{r}
blast_results <- blastSequences(dna_seq, as='data.frame', timeout=240)

print(blast_results)
```

```{r}
best_hit <- blast_results[1, ]

best_hit_id <- best_hit$Hit_id
best_hit_accession <- best_hit$Hit_accession
best_hit_species <- best_hit$Hit_def

best_hit_id
best_hit_accession
best_hit_species
```

```{r}
ref_seq <- entrez_fetch(db = "nucleotide", id = best_hit_accession, rettype = "fasta")
ref_seq <- DNAString(gsub(".*\\n", "", ref_seq))
```

```{r}
alignment <- pairwiseAlignment(dna_seq, ref_seq)
```

In conclusion, the BLAST results suggest that the patient’s DNA sequence is closely related to Yersinia pestis strain 46514, which is a known pathogenic organism. This finding warrants immediate clinical attention to determine if the patient is infected with Yersinia pestis and to implement appropriate diagnostic and treatment protocols.

I would recommend immediate testing and monitoring
